**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study.

### 2017-06-02 doc/adaAbstract.Rmd
fixed scaling problems with gee output

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
devtools::load_all()
load_data(update = TRUE)
set_options()
```

@@

gee <- ds %>%
  dplyr::mutate(
    udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
    ageBase = ifelse(fVN == "Baseline", Age, NA),
    DM = ifelse(DM == 1, "diabetes", "non_dia"),
    fDM = relevel(as.factor(DM), "non_dia"),
    Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
    Ethnicity = relevel(as.factor(Ethnicity), "Other")
  ) %>% 
  dplyr::filter(!(fVN == "Baseline" &
                    acrStatus == "Macroalbuminuria")) %>%
  dplyr::filter(!(fVN == "Baseline" & eGFRStatus == "Moderate")) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  # dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%
  mason::design("gee") %>% 
  mason::add_settings(
      family = stats::gaussian(),
      corstr = 'ar1',
      cluster.id = 'SID'
    ) %>%
  mason::add_variables("yvars", c("ACR", "eGFR")) %>% 
  mason::add_variables("xvars", "UDBP") %>% 
  mason::add_variables("covariates", c("VN", "ageBase", "Sex", "Ethnicity", "BMI", "fDM")) %>% 
  mason::construct() %>%
  mason::scrub() %>% 
  mason::polish_transform_estimates(function(x) (exp(x) - 1) * 100) %>%
  dplyr::select(Yterms, Xterms, term, estimate, conf.low, conf.high, p.value)
```

@@

gee %>% 
  dplyr::mutate(Xterms = term) %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(Yterms = factor(Yterms, 
                                levels = c("ACR", "eGFR"),
                                ordered = TRUE),
                Xterms = factor(Xterms,
                                levels = rev(c("<-Xterm",
                                           "VN",
                                           "ageBase",
                                           "SexMale",
                                           "EthnicityEuropean",
                                           "BMI",
                                           "fDMdiabetes")),
                                labels = rev(c("uVDBP",
                                           "Follow-up Duration",
                                           "Baseline Age",
                                           "Sex (male)",
                                           "Ethnicity (European)",
                                           "BMI",
                                           "Diabetes")),
                                ordered = TRUE)) %>% 
  arrange(Xterms) %>% 
  gee_plot(xlab = "Percent difference with 95% CI in outcome for every SD increase in uVDBP and covariates")
```

>>>>

```{r setup, include=FALSE}

# poster size: print at 63" x 31.5"

knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
devtools::load_all()
load_data(update = TRUE)
set_options()
```

@@

gee <- ds %>%
  dplyr::mutate(
    udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
    ageBase = ifelse(fVN == "Baseline", Age, NA),
    DM = ifelse(DM == 1, "diabetes", "non_dia"),
    fDM = relevel(as.factor(DM), "non_dia"),
    Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
    Ethnicity = relevel(as.factor(Ethnicity), "Other")
  ) %>% 
  dplyr::filter(!(fVN == "Baseline" &
                    acrStatus == "Macroalbuminuria")) %>%
  dplyr::filter(!(fVN == "Baseline" & eGFRStatus == "Moderate")) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%
  mason::design("gee") %>% 
  mason::add_settings(
      family = stats::gaussian(),
      corstr = 'ar1',
      cluster.id = 'SID'
    ) %>%
  mason::add_variables("yvars", c("ACR", "eGFR")) %>% 
  mason::add_variables("xvars", "UDBP") %>% 
  mason::add_variables("covariates", c("VN", "ageBase", "Sex", "Ethnicity", "BMI", "fDM")) %>% 
  mason::construct() %>%
  mason::scrub() %>% 
  dplyr::select(Yterms, Xterms, term, estimate, conf.low, conf.high, p.value)
```

@@

gee %>% 
  dplyr::mutate(Xterms = term) %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(Yterms = factor(Yterms, 
                                levels = c("ACR", "eGFR"),
                                ordered = TRUE),
                Xterms = factor(Xterms,
                                levels = rev(c("<-Xterm",
                                           "VN",
                                           "ageBase",
                                           "SexMale",
                                           "EthnicityEuropean",
                                           "BMI",
                                           "fDMdiabetes")),
                                labels = rev(c("uVDBP (ug/mL)",
                                           "Follow-up Duration (Years)",
                                           "Baseline Age (Years)",
                                           "Sex (male)",
                                           "Ethnicity (European)",
                                           "BMI (kg/m^2)",
                                           "Diabetes")),
                                ordered = TRUE)) %>% 
  arrange(Xterms) %>% 
  gee_plot(xlab = "Unit difference with 95% CI in outcome for every unit increase in uVDBP and covariates")
```
